Turbulence in compact to giant H~II regions

### 2022-12-12 strucfunc_paper.tex
Finish section 5.2.3

In Figure~\ref{fig:los-vs-pos} we show the
mean non-thermal line-of-sight velocity dispersion
\(\langle\sigma\los\rangle\)
(obtained from the spectral line profiles)
versus the plane-of-sky dispersion of mean velocities
\(\sigma\pos\)
(obtained from our structure function fits).
The relationship we obtain is
\( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\),
which can be compared with previous results
using different types of samples.

\citet{2011MNRAS.413..705L} surveyed
a sample of small-to-intermediate size \hii{} regions in M33,
finding
\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
for their sub-sample with higher resolution observations
(21 sources).
This is shown as the dashed line in Figure~\ref{fig:los-vs-pos},
which can be seen to be almost identical to our own result. 
Both fits are consistent with a slope of unity and an offset of
\(\SI{8}{km.s^{-1}}\).

\citet{arthur2016turbulence} calculate the relationship
between \(\langle\sigma\los\rangle\) and \(\sigma\pos\) for different optical emission lines
([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
which is shown by the dotted line in Figure~\ref{fig:los-vs-pos}.
Although this line is a fair representation of the low-\(\sigma\)
points in our sample, it fails badly for highest dispersion source,
30~Doradus.

@@

However, as pointed out by \citet{arthur2016turbulence},
the previous analysis is oversimplified since the presence
of density fluctuations (or, more generally, emissivity fluctuations)
means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
is \emph{not} independent of the 
ordered large-scale velocity gradients along the line of sight.
Indeed, the neglect of any projection smoothing for the turbulent contribution
in the \citeauthor{2011MNRAS.413..705L} analysis is equivalent to
assuming \(\delta\kappa = -1\), which \emph{requires} substantial density fluctuations. 
This leads to a third potential explanation of the
\(\sigma\pos\)--\(\sigma\los\) relationship.
In the limit that the direct contribution of
turbulent velocity fluctuations is negligible
and that \(\sigma\los\) is entirely due to expansion along the line of sight,
then the prediction is that \(\sigma\pos / \sigma\los \approx \shortsig{E} / (1 + \shortsig{E})\)
where \( \shortsig{E} = \longsig{E}\) is the RMS fractional
variation in emissivity \(\delta E\) (on scales \(\ge r_0\))
with respect to the mean emissivity \(E_0\).

In order to disentangle the relative importance
of these three mechanisms, it is necessary to consider
additional factors.
For instance, in Figure~\ref{fig:brightness-pdfs} we test
the plausibility of the third explanation given above
by comparing the ratio  \(\sigma\pos / \sigma\los \)
with the RMS fractional variation in
\ha{} surface brightness,
\( \sigma_{S/S_0} = \langle \delta S^2 \rangle^{1/2} / S_0\).
We calculate the latter from fitting a log-normal
function to the probability distribution function
of the surface brightness map after filtering out fluctuations
on scales smaller than the velocity correlation length.
The volumetric emissivity fluctuations are predicted to be
proportional to the brightness fluctuations \citep{arthur2016turbulence}:
\(\sigma_{E/E_0} = \sigma_{S/S_0} / R^{1/2}\) where \(R\)
is the 2D-to-3D variance ratio \citep{Brunt:2010b}.
For an emissivity power spectrum \(P(k) \sim k^{-3}\)
and assuming a ratio of map size to correlation length
of \(L / r_0 = 10\) (typical value from Table~\ref{tab:Res}),
we find \(R \approx 0.2\) and hence \(\sigma_{E/E_0} \approx 2 \sigma_{S/S_0}\).
% For P(k) ~ k^-3 we have R = 0.5 (1 - 1/x) / ln(x)
% where x = L / r0 if we have suppressed variations on scales < r0
% So with x = 10 (typical value) we have R = 0.2
% For k = 4 we have R = 0.25 (1 - 1/x^2) / (1 - 1/x) = 0.275
% For k = 2 we have R = 0.5 ln(x) / x = 0.115
% 
From panel 
we require high quality measurements
of a much larger sample of \hii{} regions
than have so far been obtained.
In the meantime
is most important

>>>>

In Figure~\ref{fig:los-vs-pos} we show the
mean non-thermal line-of-sight velocity dispersion
\(\langle\sigma\los\rangle\)
(obtained from the spectral line profiles)
versus the plane-of-sky dispersion of mean velocities
\(\sigma\pos\)
(obtained from our structure function fits).
The relationship we obtain is
\( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos + (7.7 \pm 2.9)\),
which can be compared with previous results
using different types of samples.
\citet{2011MNRAS.413..705L} surveyed
a sample of small-to-intermediate size \hii{} regions in M33,
finding
\(\langle \sigma_{\text{los}} \rangle = (1.04 \pm 0.14) \sigma\pos + (8.15 \pm 0.93) \)
for their sub-sample with higher resolution observations
(21 sources).
This is shown as the dashed line in Figure~\ref{fig:los-vs-pos},
which can be seen to be almost identical to our own result. 
Both fits are consistent with a slope of unity and an offset of
\(\SI{8}{km.s^{-1}}\).
\citet{arthur2016turbulence} calculate the relationship
between \(\langle\sigma\los\rangle\) and \(\sigma\pos\) for different optical emission lines
([\ion{S}{2}], [\ion{N}{2}], \ha, [\ion{O}{3}])
in the Orion Nebula, finding \(\langle\sigma\los \approx 2 \sigma\pos\rangle\),
which is shown by the dotted line in Figure~\ref{fig:los-vs-pos}.
Although this line is a fair representation of the low-\(\sigma\)
points in our sample, it fails badly for highest dispersion source,
30~Doradus.

@@

However, as pointed out by \citet{arthur2016turbulence},
the previous analysis is oversimplified since the presence
of density fluctuations (or, more generally, emissivity fluctuations)
means that the plane-of-sky dispersion of centroids \(\sigma\pos\)
is \emph{not} independent of the 
ordered large-scale velocity gradients along the line of sight.
Indeed, the neglect of any projection smoothing for the turbulent contribution
in the \citeauthor{2011MNRAS.413..705L} analysis is equivalent to
assuming \(\delta\kappa = -1\), which \emph{requires} substantial density fluctuations. 
This leads to a third potential explanation of the
\(\sigma\pos\)--\(\sigma\los\) relationship.
In the limit that the direct contribution of
turbulent velocity fluctuations is negligible
and that \(\sigma\los\) is entirely due to ordered expansion along the line of sight,
then a non-zero \(\sigma\pos\) can arise only from emissivity fluctuations,
which cause different parts of the ordered velocity field to be picked out
for different lines of sight.
A simple model of this process is explored in Appendix~\ref{sec:appar-veloc-fluct},
where a relation between the surface brightness dispersion and the apparent
velocity dispersions is derived.
This is compared with the behavior of the ratio
\(\sigma\pos / \sigma\los\) for
our observed sample in panel~i of Figure~\ref{fig:brightness-pdfs},
in which the solid and dashed lines show results for different assumptions
about the effects of velocity gradients on \(\sigma\los\).
Although the model does qualitatively reproduce the increase
in \(\sigma\pos / \sigma\los\) with increasing \(\sigma_S\), the quantitative agreement
is poor, with the model substantially overestimating the magnitude of
plane-of-sky fluctuations as compared with the line-of-sight widths.
This is evidence that the combination of a velocity gradient with
emissivity fluctuations is insufficient on its own,
and there must therefore be an additional disordered velocity component
in order to explain our observations.

In summary, our results are most consistent with a combination
of expansion and disordered motions, in which the disordered component
becomes increasingly dominant for the sources with higher velocity dispersion.
We cannot rule out a role for either projection smoothing or emissivity fluctuations,
but the contribution is probably minor in both cases.
